Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-03-08 manuscript 01/_manuscript/index.qmd
flextable table 2

```{r}
library(targets)
library(tidyverse)
library(withr)
library(here)
library(scales)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)

@@

```{r neurosurgery}
models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical))
)

@@

summary

>>>>

```{r}
library(targets)
library(tidyverse)
library(withr)
library(here)
library(scales)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)
library(flextable)

@@

```{r neurosurgery}
models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical))
)

@@

# gather odds ratios from modelsummary object
odds_ratios <- summary |> map(pluck(1))
odds_ratios[1] <- NULL

# gather credible intervals from modelsummary object
credible_ints <- summary |> map(pluck(2))
credible_ints[1] <- NULL

# gather posterior probabilities of various magnitudes of difference
neurosurgery <- models$"Neurosurgical Intervention" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

evd <- models$"External Ventricular Drain" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

trach <- models$"Tracheostomy" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

vent <- models$"Days of Mechanical Ventilation" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

dnr <- models$"DNR Order" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

wlst <- models$"Withdrawal of Life-Sustaining Therapy" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

early_wlst <- models$"Early Withdrawal of Life-Sustaining Therapy" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

# combine probability of OR > 1 (prob of difference)
prob_difference <- list(
  "Neurosurgical Intervention" = pluck(neurosurgery, 1),
  "External Ventricular Drain" = pluck(evd, 1),
  "Tracheostomy" = pluck(trach, 1),
  "Days of Mechanical Ventilation" = pluck(vent, 1),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 1),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 1),
  "DNR Order" = pluck(dnr, 1)
)

# combine % of posterior within the ROPE
rope <- list(
  "Neurosurgical Intervention" = pluck(neurosurgery, 4),
  "External Ventricular Drain" = pluck(evd, 4),
  "Tracheostomy" = pluck(trach, 4),
  "Days of Mechanical Ventilation" = pluck(vent, 4),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 4),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 4),
  "DNR Order" = pluck(dnr, 4)
)

table1 <- bind_rows(odds_ratios, credible_ints)
table2 <- bind_rows(prob_difference, rope) |> mutate(across(1:7, as.character))

ult_table <- bind_rows(table1, table2)

ult_table <- as_tibble(t(ult_table))

tibble_2 <- as_tibble(table_2) |> select(-1)

tibble_2

column_names <- c(
  "Neurosurgical Intervention",
  "External Ventricular Drain",
  "Tracheostomy",
  "Days of Mechanical Ventilation",
  "Withdrawal of Life-Sustaining Therapy",
  "Early Withdrawal of Life-Sustaining Therapy",
  "DNR Order"
)

combined <- bind_cols(column_names, tibble_2, ult_table) |>
  rename(
    "Outcome" = ...1,
    "aOR" = V1,
    "95% Credible Interval" = V2,
    "Probability of Difference (aOR >1)" = V3,
    "% ROPE" = V4
  )

flextable(combined)
```

### 2024-03-08 manuscript 01/index.qmd
flextable table 2

```{r}
library(targets)
library(tidyverse)
library(withr)
library(here)
library(scales)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)

@@

```{r neurosurgery}
neurosurgery_mod <- with_dir(here(), tar_read(m_posterior_neurosurgery_canonical))

models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical))
)

@@

ult_table <- t(ult_table)
```

>>>>

```{r}
library(targets)
library(tidyverse)
library(withr)
library(here)
library(scales)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)
library(flextable)

@@

```{r neurosurgery}
models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical))
)

@@

ult_table <- as_tibble(t(ult_table))

tibble_2 <- as_tibble(table_2) |> select(-1)

column_names <- c(
  "Neurosurgical Intervention",
  "External Ventricular Drain",
  "Tracheostomy",
  "Days of Mechanical Ventilation",
  "Withdrawal of Life-Sustaining Therapy",
  "Early Withdrawal of Life-Sustaining Therapy",
  "DNR Order"
)

combined <- bind_cols(column_names, tibble_2, ult_table) |>
  rename(
    "Outcome" = ...1,
    "aOR" = V1,
    "95% Credible Interval" = V2,
    "Probability of Difference (aOR >1)" = V3,
    "% ROPE" = V4
  )

vector <- as.numeric(noquote(unlist(odds_ratios, use.names = FALSE)))

flextable(combined)
get_flextable_defaults()
